\section{Assignment-3}

\begin{question}{}{}
    Please finish the BBC video and build your vocabulary about cuizine when reviewing the 3 videos in this unit.
\end{question}

\begin{longtable}{|p{7cm}|p{7cm}|}
    \caption{Vocabulary About Cuisine} \label{tab:vocab_cuisine} \\
    \hline
    \textbf{English} & \textbf{Chinese} \\
    \hline
    \endfirsthead
    
    \caption[]{Vocabulary About Cuisine (continued)} \\
    \hline
    
    \endhead
    
    \hline
    \endfoot
    
    \hline
    \endlastfoot
    
    \multicolumn{2}{c}{\textbf{Influencing Factors}} \\ \hline
    geographical conditions & 地理条件 \\ \hline
    environment and climate diversity & 环境和气候多样性 \\ \hline
    people have wheaten food in the north of China and rice in the south & 南米北面 \\ \hline
    
    \multicolumn{2}{c}{\textbf{Four Flavors}} \\ \hline
    \textbf{Bashu} & \textbf{Qilu} \\ \hline
    Shredded Pork with Chili and Soy (麻婆豆腐) & Braised Whelk with Brown Sauce (红烧海螺) \\ \hline
    Tea-leaf and Camphor Smoked Duck (樟茶鸭) & Fried Pork Joint (锅烧肘子) \\ \hline
    Sauted Chicken Cubes with Chilli and Peanuts (宫保鸡丁) & Fried Tofu with Egg Wrapping (锅塌豆腐) \\ \hline
    Stewed Bean Curd with Minced Pork in Pepper Sauce (鱼香肉丝) & Quick-fried Mutton with Green Onion (葱爆羊肉) \\ \hline
    ~ & ~ \\ \hline
    \textbf{Huaiyang} & \textbf{Yuemin} \\ \hline
    Braised Shredded Chicken with Ham and Dried Tofu (大煮干丝) & Soup Simmered inside a Whole Winter Melon (冬瓜盅) \\ \hline
    Sweet and Sour Mandarin Fish (松鼠桂鱼) & Fried Pork with Pineapple (菠萝古老肉) \\ \hline
    Beggar's Chicken (叫花鸡) & Steamed Rice with Dried Duck (腊味煲仔饭) \\ \hline
    The Lion’s Head (the Meatball) in Yangzhou Style (淮扬狮子头) & Buddha Jumps over the Wall (佛跳墙) \\ \hline
    
    \multicolumn{2}{c}{\textbf{Relevant Terminology}} \\ \hline
    The Staple Food & 主食 \\ \hline
    The Flavors & 风味 \\ \hline
    The Nutrition Structure & 饮食结构 \\ \hline
    Wheaten food & 面食 \\ \hline
    vegetarian diet & 素食 \\ \hline
    household dishes & 家常菜 \\ \hline
    complete presence of color, aroma and taste & 色香味有严格的要求 \\ \hline
    street food & 街边小吃 \\ \hline
    
    \multicolumn{2}{c}{\textbf{Adjectives for Dish Names}} \\ \hline
    skillful and delightful & 出神入化 \\ \hline
    suits both refined and popular tastes & 雅俗共赏 \\ \hline
    
    \multicolumn{2}{c}{\textbf{The Staple Food}} \\ \hline
    Sichuan & ~ \\ \hline
    Rice & 米饭 \\ \hline
    Rice Porridge & 粥 \\ \hline
    Rice Cake & 米糕 \\ \hline
    Steamed Vermicelli Roll & 肠粉 \\ \hline
    Guilin Rice Noodles & 桂林米粉 \\ \hline
    Stir-fried Rice Noodles with Beef & 干炒牛河 \\ \hline
    GuiYang Spring Roll & 丝娃娃 \\ \hline
    red oil hot pot & 红油火锅 \\ \hline
    Fish Filets in Hot Chilli Oil & 水煮鱼 \\ \hline
    spicy hot pot/Malatang & 麻辣烫 \\ \hline
    hot pot & 火锅 \\ \hline
    chuanchuan & 串串 \\ \hline
    ~ & ~ \\ \hline
    Northeast of China & ~ \\ \hline
    pickled cabbage & 酸菜 \\ \hline
    Fat Pork with Pickled Cabbage & 酸菜白肉 \\ \hline
    Pork and Pickled Cabbage dumplings & 猪肉酸菜水饺 \\ \hline
    ~ & ~ \\ \hline
    south of China & ~ \\ \hline
    Sweet and Sour Mandarin Fish & 松鼠桂鱼 \\ \hline
    Square Pork with sauce & 酱方 \\ \hline
    Fresh Pork and Salted Pork with Bamboo Shoot Soup & 腌笃鲜 \\ \hline
    Osmanthus Jelly & 桂花糕 \\ \hline
    ~ & ~ \\ \hline
    meat & ~ \\ \hline
    braised pork & 红烧肉 \\ \hline
    ~ & ~ \\ \hline
    Candied Sweet Potato & 拔丝地瓜 \\ \hline
    Fish in Sour Soup & 酸汤鱼 \\ \hline
    Salt Baked Razor Clam & 盐焗蛏子 \\ \hline
    Chicken Cubes with Chili Peppers & 辣子鸡丁 \\ \hline
    Balsam Pear Scrambled eggs & 苦瓜炒蛋 \\ \hline
    ~ & ~ \\ \hline
    fried rice & 炒饭 \\ \hline
    fried noodles & 炒面 \\ \hline
    Beijing roast duck & 北京烤鸭 \\ \hline
    Xiao long bao & 小笼包 \\ \hline
    Kung Pao Chicken & 宫保鸡丁 \\ \hline
    Boluo gulao rou (Sweet and sour pork with pineapple) & 菠萝古老肉 \\ \hline
    Fried shrimps with cashew nuts & 腰果炒虾仁 \\ \hline
    Stir-fried tofu in hot sauce/Ma po doufu & 麻婆豆腐 \\ \hline
    ~ & ~ \\ \hline
    Dongpo soup & 东坡羹 \\ \hline
    Dongpo Pork & 东坡肉 \\ \hline
    ~ & ~ \\ \hline
    Lamb Spine Hot Pot & 羊蝎子 \\ \hline
    ~ & ~ \\ \hline
    cornmeal pancake & 玉米饼 \\ \hline
    
    \multicolumn{2}{c}{\textbf{The Flavors}} \\ \hline
    Sichaun & spicy \\ \hline
    Northeast of China & sour \\ \hline
    south of China & sweetness \\ \hline
    ~ & ~ \\ \hline
    bitter & 苦 \\ \hline
    salty & 咸 \\ \hline
    ~ & ~ \\ \hline
    turns out to have a sour & 酸味绵柔 \\ \hline
    tender and crispy taste & 松软清脆 \\ \hline
    crispy outside and tender inside & 外脆里嫩 \\ \hline
    provides a sour and sweet taste & 酸甜可口 \\ \hline
    pungent & 刺激性的 \\ \hline
    fragrant & 清香的 \\ \hline
    mellow & 醇美的 \\ \hline
    Juicy & 多汁的 \\ \hline
    Greasy & 油腻 \\ \hline
    
    \multicolumn{2}{c}{\textbf{Wheaten Food}} \\ \hline
    north & ~ \\ \hline
    Dumplings & 饺子 \\ \hline
    Fried Noodles & 炒面 \\ \hline
    steamed Bings & 包子 \\ \hline
    Shandong Pancake & 山东煎饼 \\ \hline
    Fried Dumplings & 锅贴 \\ \hline
    south & ~ \\ \hline
    shao-mai & 烧麦 \\ \hline
    spring rolls & 春卷 \\ \hline
    fried dough sticks & 油条 \\ \hline
    
    \multicolumn{2}{c}{\textbf{Ingredients}} \\ \hline
    pepper & 辣椒 \\ \hline
    cabbage & 大白菜 \\ \hline
    prickly ash & 花椒 \\ \hline
    mandarin fish & 桂鱼 \\ \hline
    Wheat & 小麦 \\ \hline
    ~ & ~ \\ \hline
    meat & ~ \\ \hline
    pork & 猪肉 \\ \hline
    fish & 鱼肉 \\ \hline
    chicken & 鸡肉 \\ \hline
    duck & 鸭肉 \\ \hline
    ~ & ~ \\ \hline
    vegetarian food & ~ \\ \hline
    water shield & 茆(莼菜) \\ \hline
    lentil & 荏菽(扁豆) \\ \hline
    day lily & 谖草 (黄花菜) \\ \hline
    mulberry & 桑葚 \\ \hline
    ~ & ~ \\ \hline
    the spine of the lamb & 羊脊骨 \\ \hline
    ~ & ~ \\ \hline
    Mild green chillies & 青椒 \\ \hline
    ginger & 生姜 \\ \hline
    garlic & 大蒜 \\ \hline
    aubergine & 茄子 \\ \hline
    cucumber & 黄瓜 \\ \hline
    peanut & 花生 \\ \hline
    ~ & ~ \\ \hline
    a piece of flour pancake & 一张面皮 \\ \hline
    
    \multicolumn{2}{c}{\textbf{Seasonings}} \\ \hline
    salt & 盐 \\ \hline
    red sauce & 酱油 \\ \hline
    dark soy sauce & 黑酱油/老抽 \\ \hline
    
    \multicolumn{2}{c}{\textbf{Food Preparation Methods}} \\ \hline
    natural fermentation & 自然发酵 \\ \hline
    pickled & 腌制 \\ \hline
    braise & 炖 \\ \hline
    toss & 拌 \\ \hline
    chop & 剁 \\ \hline
    shred & 切 \\ \hline
    slice & 割 \\ \hline
    dice & 削 \\ \hline
    ~ & ~ \\ \hline
    cooking utensils & ~ \\ \hline
    cleaver & 菜刀 \\ \hline
    rolling pin & 擀面杖 \\ \hline
    
    \multicolumn{2}{c}{\textbf{Drinks}} \\ \hline
    Tea & 茶 \\ \hline
    
    \multicolumn{2}{c}{\textbf{Elegant Names for Dishes}} \\ \hline
    Appetizers combination & 八方宾客(富贵八小碟) \\ \hline
    Beggars chicken & 名扬天下(新派叫花鸡) \\ \hline
    Double-boiled duck with lotus seed & 大展宏图(鲜莲子炖老鸭) \\ \hline
    Braised vegetable with mushroom & 包罗万象(鲜鲍菇扒时蔬) \\ \hline
    Deep-fried prawn with almond & 紧密合作(杏仁大明虾) \\ \hline
    Braised seasonal vegetable, Beijing style & 风景如画(京扒扇形蔬) \\ \hline
    Pan-fried Australian beef with black pepper & 共谋发展(黑椒澳洲牛柳) \\ \hline
    Fried rice with minced beef & 携手共赢(生炒牛松饭) \\ \hline
    Roasted lamb chop with cumin & 干秋盛世(孜然烤羊排) \\ \hline
    Chinese petit fours & 共建和平(美点映双辉) \\ \hline
    Seasonal fresh fruit platter & 承载梦想(环球鲜果盆) \\ \hline
    ~ & ~ \\ \hline
    Ant climbing trees & 蚂蚁上树 \\ \hline
    Lion's head & 狮子头 \\ \hline
    Treasures filling the home & 金玉满堂 \\ \hline
    A flight of white egrets in blue sky & 一行白鹭上青天 \\ \hline
    The grasses up north are as blue as jade & 燕草如碧丝 \\ \hline
    A timely snow promising a good harvest & 瑞雪兆丰年 \\ \hline
    
\end{longtable}

\begin{question}{}{}
    Please prepare one menu for a foreign student who comes to China for the first time.
\end{question}

\begin{longtable}{|p{2cm}|p{2cm}|p{5cm}|p{5cm}|}
    \caption{Menu} \\
    \hline
    \multicolumn{4}{|c|}{\textbf{Varieties of dishes}} \\
    \hline
    \textbf{Varieties of dishes} & \textbf{Dish name} & \textbf{Dish description} & \textbf{Tips} \\
    \hline
    \endfirsthead
    
    \caption[]{(续上) Menu} \\
    \hline
    \multicolumn{4}{|c|}{\textbf{Varieties of dishes}} \\
    \hline
    \textbf{Varieties of dishes} & \textbf{Dish name} & \textbf{Dish description} & \textbf{Tips} \\
    \hline
    \endhead
    
    \hline
    \endfoot
    
    \hline
    \endlastfoot
    
    Meat Dishes & ~ & ~ & These dishes are not halal. Muslim patrons may wish to choose other options. \\ \hline
    ~ & General Tso's Chicken(左宗棠鸡) & A popular chicken dish in American-Chinese cuisine known for its sweet and sour flavors, typically served with vegetables and sauce. & ~ \\ \hline
    ~ & Orange Chicken(橙子鸡) & A beloved Chinese dish featuring crispy chicken pieces coated in flour and fried until golden brown, then smothered in a tangy orange sauce. & ~ \\ \hline
    ~ & Black Pepper Chicken(黑胡椒鸡) & A stir-fried chicken dish seasoned with black pepper, usually paired with onions and other vegetables, characterized by its spicy and robust black pepper aroma. & Spiciness level can be adjusted. \\ \hline
    ~ & Szechuan Beef(四川牛肉) & A spicy Sichuan-style beef dish cooked with chili peppers and Sichuan peppercorns, giving it a numbing and fiery flavor profile. & ~ \\ \hline
    ~ & Beef \& Broccoli(西兰花炒牛肉) & A classic combination of tender beef strips and fresh broccoli florets stir-fried in a savory sauce, commonly found in Chinese-American cuisine. & ~ \\ \hline
    Staple Foods & ~ & ~ & ~ \\ \hline
    ~ & fried rice(炒饭) & A versatile dish made by frying cooked rice with various ingredients such as vegetables, meat, and sometimes eggs, resulting in a flavorful and filling meal. & ~ \\ \hline
    ~ & scallion pancakes(葱油饼) & Flaky flatbreads filled with scallions and brushed with sesame oil, often served as a side dish or appetizer in Chinese cuisine. & ~ \\ \hline
    ~ & Soup Dumplings (汤饺) & Steamed dumplings filled with juicy pork and broth, typically enjoyed by sipping the soup inside before eating the dough and filling. & ~ \\ \hline
    ~ & Shrimp Kung Pao Noodles(宫保虾粉) & A spicy noodle dish featuring shrimp cooked in a Kung Pao sauce, which includes peanuts, chili peppers, and Sichuan peppercorns. & Caution: Contains seafood. Not recommended for those with seafood allergies. \\ \hline
    ~ & Pan-Fried Noodles in Superior Soy Sauce(酱油炒面) & Wok-tossed noodles mixed with a rich soy-based sauce, creating a deliciously savory and slightly sweet flavor. & ~ \\ \hline
    Soups and Beverages & ~ & ~ & ~ \\ \hline
    ~ & wonton soup(馄饨汤) & A comforting soup made with small, stuffed wontons, typically filled with pork or shrimp, and served in a clear broth with vegetables. & ~ \\ \hline
    ~ & Tea(茶) & A wide range of tea varieties, from green to black, oolong to white, each offering unique flavors and health benefits. & ~ \\ \hline
    ~ & Rice Wine(米酒) & An alcoholic beverage made from fermented rice, often consumed as a digestif or used in cooking to add depth and complexity to dishes. & ~ \\ \hline
    Vegetarian Dishes & ~ & ~ & ~ \\ \hline
    ~ & Bang Bang Broccoli(西兰花) & A spicy and sweet dish featuring broccoli florets tossed in a bang bang sauce, a blend of sweet chili sauce, mayonnaise, and other seasonings. & ~ \\ \hline
    ~ & Candied Sweet Potato(拔丝地瓜) & A dessert dish where sweet potatoes are deep-fried and coated in a caramelized sugar glaze, providing a crunchy exterior and soft interior. & ~ \\ \hline
    ~ & cornmeal pancake(玉米饼) & A flatbread made from cornmeal, often served as a side dish or used as a wrap for various fillings. & ~ \\ \hline
    ~ & Soup Simmered inside a Whole Winter Melon(冬瓜盅) & A hearty soup prepared by simmering winter melon rind with various meats and vegetables, resulting in a fragrant and nourishing broth. & ~ \\ \hline
    ~ & The grasses up north are as blue as jade(燕草如碧丝) & A poetic reference to the lush green grasses in northern regions, often used metaphorically to describe beauty or abundance. & ~ \\ \hline
    Others & ~ & ~ & ~ \\ \hline
    ~ & egg rolls(蛋卷) & Crispy spring rolls filled with vegetables, meat, and sometimes noodles, typically served as an appetizer or snack. & Caution: Contains eggs. Not recommended for those with egg allergies. \\ \hline
    ~ & Osmanthus Jelly(桂花糕) & A delicate jelly-like dessert made with osmanthus flowers, often served chilled and garnished with syrup for a refreshing treat. & ~ \\ \hline
    ~ & Xiao long bao(小笼包) & Delicate steamed dumplings filled with pork and soup, best enjoyed by biting a small hole first to release the hot broth within. & Bite a small hole first to let the hot broth escape before consuming the entire dumpling. \\ \hline
    ~ & Square Pork with sauce(酱方) & A braised pork belly dish slow-cooked in a soy-based sauce, resulting in tender meat with a rich, savory flavor. & ~ \\ \hline
\end{longtable}

