\section{Chinese to English}

\begin{part}{}{}
    中国的众多少数民族也有丰富多彩的节日， 著名的有：藏族的藏历新年、 蒙古族的那达慕、傣族的泼水节、傈僳族的刀杆节、彝族的火把节、白族的三月节、信仰伊斯兰教的民族的古尔邦节等。

    Many ethnic groups also have varieties of festivals, among which are the Tibetan New Year of Tibetan people, the Naadam of the Mongolians, the Water Splashing Festival of the Dai people, the Knife-Pole Festival of Lisu people, the Firebrand Festival of the Yi people, March Fair of Bai people, the Corban Festival of the Islamic group.
\end{part}

\begin{part}{}{}
    春节要大扫除、打爆竹、用红色装饰房子、守岁。中国人对自然特别亲近， 尤其是对月亮。中秋节的月亮是一年中最大最圆的，“圆”象征团圆， 所以中秋节是家人团圆的日子。

    On the Spring Festival, people would clean the house, set off firecrackers and fireworks, decorate the house with reds and stay up late. Chinese people are very close to nature, especially with the moon. The moon on the Mid-Autumn Festival turns out to be the fullest of the year. And given that fullness in Chinese culture is a symbol of union, the Mid-Autumn Festival thus became the festival for family reunion.
\end{part}

\begin{part}{}{}
    在你身上，我能看到他那把剑的影子，但或许那些影响太过沉重了，你不能让你父亲的身影限制你，你得好好培养你的天赋。宇宙万物皆统一于气，人亦由气化生，但唯有赤子之心方能使人气合一，从而铸就伟大的战士，其徐如林，侵掠如火。

    In you, I see the shadow of his sword. Perhaps this shadow falls heavy on your shoulders. You can't allow your father's legacy to hold you back. You need to cultivate your gift. The chi pervades the universe and all living things. We are all born with it. But only the most true will connect deeply to his chi and become a great warrior. Tranquil as a forest but on fire within.
\end{part}