\section{Chinese food}

\begin{question}{}{}
    Design a case to introduce \textbf{Chinese food} to your foreign friend who just arrives in Shanghai.(200-300 words).
\end{question}

Welcome to Shanghai, China! I'm glad to hear that you are interested in Chinese food. Overall, \textbf{Chinese cuisine is incredibly diverse}, offering a wide range of flavors and a balanced mix of meat and vegetables. I believe there will be something to suit your taste, but I would like to recommend a menu of Chinese dishes that I think you will enjoy.

The first dish I want to recommend is \textbf{fried rice}. It is made by frying rice and mixing it with various ingredients. You can choose what you want to add to your dish. If you prefer noodles instead of rice, we have \textbf{fried noodles}. If you enjoy a mix of different ingredients, you can try \textbf{Malatang}. It is a combination of your favorite vegetables and meat cooked in a delicious broth.

Since you are not Muslim, the next dish I recommend is \textbf{Beijing roast duck}. \textit{Beijing roast duck is tender and juicy with a rich flavor, but enjoying it properly requires a specific method.} The right way to eat Beijing roast duck is to take a piece of flour pancake, spread some sauce on it, and then add a small serving of the duck skin, meat, and vegetables. Roll everything up and enjoy the delicious taste. \textbf{Don't miss this dish!}

Next, I recommend a local Shanghai specialty, \textbf{shengjian}, also known as pan-fried bao. \textit{Pan-fried bao consists of small buns filled with pork and a burst of savory soup.} The buns are cooked in a flat pan with water and oil, resulting in a golden, crispy bottom and a soft, fluffy top. To enjoy pan-fried bao, use chopsticks or a fork to pick up the bun. Take a small bite at the top to make a hole, then sip the hot soup inside to prevent burning. After sipping the soup, eat the remaining bun, which has a crispy bottom and a soft, savory filling.

For drinks, you can try \textbf{tea}. You might have had tea in the United States, but it would be great to taste some authentic Chinese tea.

Additionally, if you are not a fan of spicy food, you can request a lower level of spiciness when ordering.

If you have the time, let's meet up and have Chinese food at \textbf{Hongji Plaza}, which is near Shanghai University.
