\section{Qingming}

\begin{question}
    Design a case to introduce \textbf{Qingming} to your foreign friend who just arrives in Shanghai.(200-300 words).
\end{question}

\textbf{Welcome to Shanghai, China!} I heard you are very interested in China's \textbf{Qingming Festival}, so let me give you a brief introduction. I hope it will be helpful.

\textbf{Similar to your April Fool's Day}, Qingming Festival, also known as \textbf{Tomb Sweeping Day}, falls around April 4 or 5. It is a time for people to reflect and remember family members who have passed away by visiting their tombs to clean and pay respects. The festival has been observed by Chinese people for over 2,500 years, dating back to when emperors would hold ceremonies to honor their ancestors.

Do you enjoy outings or flying kites? These are also customs of the \textbf{Qingming Festival}. Today, people pay their respects by visiting and sweeping the graves of their relatives, leaving offerings, burning incense, and paper money. In recent years, people have been burning essentials of the afterlife, such as cars and iPhones. The day is also regarded as the start of spring, when people go outside to enjoy the blossoming spring and special Qingming foods like \textbf{green rice balls}. I personally love green rice balls and hope you will enjoy them too.

To truly understand this festival, we need to look at the \textbf{Cold Food Festival}. There is an interesting story about the Cold Food Festival. It memorializes \textbf{Jie Zitui}, who made a broth from his own flesh (\textit{incredible, isn't it?}) for Prince Chong'er during his exile. When the prince became king, he forgot about Jie and gave positions to other officials. Jie, not minding, moved to a remote mountain with his mother. When the king realized his mistake, he went to find Jie but couldn't persuade him to come down from the mountain. The king set fire to the mountain, and Jie was found dead under a tree with his mother on his back. The king ordered no fire to be set on this day to remember Jie's sacrifice, leading to the \textbf{Cold Food Festival}. Over time, Chinese ancestors extended these practices into \textbf{Qingming}, and people eventually combined them into a single day.

Spring is just a few months away. If you are interested, let's go kite flying at the \textbf{Shanghai International Kite Flying Field in Fengxian Bay}. We can then make green rice balls together.